Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-19 paper.tex
Clarify a sentence in RPINF

With this setup, two expressions $t$ and $u$ are definitionally equal at reducible transparency if and only if their RPINFs, $t'$ and $u'$, are syntactically equal except for those subexpressions marked as proofs.
This notion of equality is syntactic, so it can be checked quickly and we can define an effective hash function that is compatible with it.
This allows us to use a hash map for the instantiations while still comparing them up to definitional equality.

>>>>

With this setup, two expressions $t$ and $u$ are definitionally equal at reducible transparency if and only if their RPINFs are syntactically equal except for the marked proof subexpressions.
This notion of equality is syntactic, so it can be checked quickly and we can define an effective hash function that is compatible with it.
This allows us to use a hash map for the instantiations while still comparing them up to definitional equality.
